Constant Error Tolerance Computational Fuzzy Extractors

### 2014-01-13 trunk/constantRate/ConstCompFuzzExt.tex
Added notes on problems with the proof

@@

\section{A Constant Rate Computational Fuzzy Extractor}

@@

\subsection{Parameter Discussion}
Security of \consref{cons:first construction} relies on a large number of dimensions which are unpredictable.  Correction occurs for a small number of dimensions that are allowed to vary completely.  As described in \secref{sec:supported sources}, \consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries~(meaning they have min-entropy).

To show that $gap$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.  We allow $t$ errors with an alphabet of size $2^n$.  This means that
\begin{align*}
\log |B_t| &= \log \sum_{i=0}^t {\ell \choose i} (2^n-1)^i\\
&> \log {\ell \choose t} (2^n-1)^t\\
&=\Omega(tn) + \log {\ell\choose t}
% \log (2^n)^{H_{2^n}(t/\ell)\ell - o(\ell)} =n( H_{2^n}(t/\ell)\ell -o(\ell) )
\end{align*}
\bnote{Need a good bound on ${\ell \choose t}$.}
We now ask how much entropy is necessary for security.  The first presented type of source was where each block was independent and had super-logarithmic min-entropy.  This means that $\Hoo(W) \approx \ell \omega(\log n)$.  Thus in the setting where $t = \omega(\ell)$ we obtain that 
\[
gap = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \omega(\ell n) + \log {\ell \choose t}\right)< 0. 
\]
This \consref{cons:first construction} is the first fuzzy extractor with a negative $gap$.\footnote{We can make gap smaller by recalling that note every block must contribute fresh entropy.  If each block is derived from a single source with super-logarithmic entropy then the starting entropy need only be $\omega(\log n)$.}

\textbf{Note:} If $t = o(\ell)$ then the value of $gap$ is not clear, there are some $\ell$ for which it will be negative.  However in the setting where $n>>\ell$ and a constant number of errors are being corrected $gap$ may be positive.  However, we extract from at most $\ell$ bits and thus need $\ell$ to be large enough for reasonable application security.  Setting $ \ell , t, n$ all of roughly the same size provides a natural balance of parameters.

>>>>

The remainder is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries} , describe computational fuzzy extractors in \secref{sec:fuzzy extractors}, present our construction in \secref{sec:construction} and discuss parameters and tradeoffs in \secref{sec:discussion}.

@@

\section{A Constant Rate Computational Fuzzy Extractor}
\label{sec:construction}

@@

\section{Discussion}
\label{sec:discussion}
Security of \consref{cons:first construction} relies on a large number of dimensions which are unpredictable.  Correction occurs for a small number of dimensions that are allowed to vary completely.  As described in \secref{sec:supported sources}, \consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries~(meaning they have min-entropy).

To show that $gap$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.  We allow $t$ errors with an alphabet of size $2^n$.  This means that
\begin{align*}
\log |B_t| &= \log \sum_{i=0}^t {\ell \choose i} (2^n-1)^i\\
&> \log {\ell \choose t} (2^n-1)^t\\
&=\Theta(tn) + \log {\ell\choose t}
% \log (2^n)^{H_{2^n}(t/\ell)\ell - o(\ell)} =n( H_{2^n}(t/\ell)\ell -o(\ell) )
\end{align*}
\bnote{Need a good bound on ${\ell \choose t}$.}
We now ask how much entropy is necessary for security.  The type of source we considered was independent blocks each with super-logarithmic min-entropy.  This yields 
\[
gap = \Hoo(W) - \log |B_t| < \ell \omega(\log n) -\left( \Theta(t n) + \log {\ell \choose t}\right). 
\]
When $t =\Theta(\ell)$, then $gap<0$ and the output entropy is $|C| - \ngl(n)$~(if $C$ is a constant rate, this is $\Theta(\ell)$).
Thus, \consref{cons:first construction} achieves negative $gap$ when $t = \Theta(\ell)$.  Furthermore, not every block must contribute entropy, so security is possible when the total starting entropy is $\omega(\log n)$.  For example, \consref{cons:first construction} is secure when each block is equal and drawn from a distribution of super-logarithmic min-entropy.  So there are supported sources with negative $gap$ for any value of $t$.  We achieve $gap<0$, constant error tolerance, and extract a constant fraction of $n$ when $t = \Theta(\ell)$ and $\ell = O(n)$.
%When $ \ell , t, n$ to be the same order provides a natural balance of parameters.
